---
title: "CIVE3750 Data Visualisation"
author: "Marco-Felipe King"
date: '2022-11-15'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(ggplot2)
require(dplyr)
require(tidyr)
require(hrbrthemes)
```

## Boxplots vs Violins!

This is going to be a boxplot of mtcars horsepower vs cylinders and I will colour by cylinder number.

```{r mtcars}

mtcars %>% 
  ggplot()+
  geom_violin(aes(x=as.factor(cyl),y=hp,fill=as.factor(cyl)),draw_quantiles = c(0.25,0.5,0.75))+
  geom_jitter(aes(x=as.factor(cyl),y=hp),height = 0, width=0.1,alpha=0.5)+
  hrbrthemes::theme_ipsum(axis_text_size = 14,axis_title_size = 14)+
  xlab("Number of cylinders")+
  ylab("Horsepower")+
  scale_fill_brewer(palette = "Set1")+
  theme(legend.position = " ") -> v

```

# Boxplots

```{r boxplots this time}

mtcars %>% 
  ggplot()+
  geom_boxplot(aes(x=as.factor(cyl),y=hp,fill=as.factor(cyl)))+
  geom_jitter(aes(x=as.factor(cyl),y=hp),height = 0, width=0.1,alpha=0.5)+
  hrbrthemes::theme_ipsum(axis_text_size = 14,axis_title_size = 14)+
  xlab("Number of cylinders")+
  ylab("Horsepower")+
  scale_fill_brewer(palette = "Set1")+
  theme(legend.position = " ") -> b

```

# Put them together in the same graph

```{r}
ggpubr::ggarrange(b,v,ncol = 2,legend = "none",common.legend = TRUE,labels = c("a) Boxplots","b) Violin plots"))
```
### ANOVA of cylinders on hp

```{r}
aov(data=mtcars,hp~as.factor(cyl)) %>% broom::tidy()
```

## Continuous predictor
```{r}

mtcars %>% 
  ggplot()+
  geom_point(aes(x=disp,y=hp,colour=as.factor(cyl)))+
  geom_smooth(aes(x=disp,y=hp,colour=as.factor(cyl)),method="lm")+  
  scale_color_brewer(palette = "Set1")+
  hrbrthemes::theme_ipsum(axis_text_size = 14,axis_title_size = 14)+
  xlab("Number of cylinders")+
  ylab("Horsepower")+
  scale_fill_brewer(palette = "Set1")+
  theme(legend.position = " ")
```

# An ANOVA to test the effect of number of cylinders on hp
```{r}

my_anova <- aov(data=mtcars, hp~as.factor(cyl))

summary(my_anova)

```

Lets plot the residuals

```{r}
plot(my_anova)
```


## Plot a continuous predictor against a continuous response

```{r}

df <- read.csv("~/Downloads/concrete_data.csv.xls")
df <- df %>% janitor::clean_names()
  df
```

```{r}
df %>% 
  pivot_longer(!strength) %>% 
  ggplot()+
  geom_point(aes(x=value,y=strength,colour=name),alpha=0.05)+
  geom_smooth(aes(x=value,y=strength,colour=name),method="lm")+
  facet_wrap(~name,scales="free")+
  theme_ipsum()+
  scale_color_brewer(palette = "Set2")+
  theme(legend.position = " ")
  
```

## Linear regression model to predict strength

```{r}

lm_strength <- lm(data=df,strength~.)

summary(lm_strength)
```
